### 2019-06-22 Memoria/Chapters/Introduction.tex
Escrito capitulo 2
Capitulo tres de la memoria empezado

Thus, the human learning process is a slow and tedious process. So, do we want to teach machines to learn the way humans do? Machines have proven to be outstanding at repetitive tasks, as well as they reach calculation speeds that humans can only dream of. It is worth asking if it is possible to develop a learning method for machines that is orders of magnitude faster than the human and equal or more effective. Although there is a major impediment to the development of such a method: we do not know if it exists! The search for a method to avoid the disadvantages of the human learning process is what drives research in the science we know today as \acf{ML}.

@@

\acs{ML} is a field derived from computer science, and a branch of \acf{AI}, whose ultimate goal is to develop methods that make it possible for machines to learn. In other words, the techniques embedded in \acs{ML} aim to develop programs that guide computers to learn from a set of examples. \acs{ML} is part of \acs{AI} in the sense that \acs{AI} is often directed at simulating human beings behavior through computers, so that we can better understand how humans work and help them.

\subsection{Types of Machine Learning}

There are several approaches within the field of \acf{ML}, these are classified according to the information that is provided to the machine for it to learn. Thus, following the classification proposed in \cite{ayodele2010types}, we find four different types of learning:

>>>>

Thus, the human learning process is a slow and tedious process. So, do we want to teach machines to learn the way humans do? Machines have proven to be outstanding at repetitive tasks, as well as they reach calculation speeds that humans can only dream of. It is worth asking if it is possible to develop a learning method for machines that is orders of magnitude faster than the human and equal or more effective. Although there is a major impediment to the development of such a method: we do not know if it exists! The search for a method to avoid the disadvantages of the human learning process is what drives research in the science we know today as \textit{machine learning}.

@@

Machine learning is a field derived from computer science, and a branch of \acf{AI}, whose ultimate goal is to develop methods that make it possible for machines to learn. In other words, the techniques embedded in machine learning aim to develop programs that guide computers to learn from a set of examples. Machine learning is part of \acs{AI} in the sense that \acs{AI} is often directed at simulating human beings behavior through computers, so that we can better understand how humans work and help them.

\subsection{Types of Machine Learning} \label{sec:TypesOfML}

There are several approaches within the field of machine learning, these are classified according to the information that is provided to the machine for it to learn. Thus, following the classification proposed in \cite{ayodele2010types}, we find four different types of learning:
